---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Alexis Kulbacki"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
# load library
library(tidyverse)
```

<br><br>

## Introduction

```{r read-examine-data}
# reading in the data 
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv")
```

<br><br>

## Question 1

#### In Japan, what style of packaging is liked the least?

### Methods
```{r}
# view the data
glimpse(ramen_ratings)

# pipe in the data from ramen_ratings
ramen_ratings %>%
  # drop rows with no answer available for stars
   drop_na(stars) %>%
  # filter the country to be Japan
  filter(country == "Japan") %>%
  # select specific rows, in this case stars and country 
  select(stars, country, style) %>% 
  # ggplot function
  ggplot() + 
  # places style on the x-axis
  aes(x = style) + 
  # makes a histogram
  geom_histogram(stat = "count")
  

```
### Answer

In Japan, box is the style that is liked the least.


<br><br>

## Question 2

#### In China, what packaging style of ramen seems to be the favorite?

### Methods
```{r}
# pipe in the data from ramen_ratings
ramen_ratings %>%
  # drops rows with no answers available for style
  drop_na(style) %>%
  # filters the country to be China
  filter(country == "China") %>%
  # ggplot function
  ggplot() + 
  # style on x axis  
  aes(x = style) +
  # make a histogram  
  geom_bar(stat = "count", color = "black", fill = "pink") +
  labs(x= "style") +
  # add non-default theme of choice
  theme_bw() 


```
### Answer

In China, the ramen packaging style that most people seem to like is pack.

<br><br>

## Question 3

#### What brands of ramen does Australia have?

### Methods
```{r}
# pipe in the data from ramen_ratings
ramen_ratings %>%
  # drops rows with no answers available for brand
  drop_na(brand) %>%
  # fitlers the country to be Australia
  filter(country == "Australia") %>%
  # selects just rows that are the brand
  select(brand) %>%
  # ggplot function
  ggplot() + 
  # style on x axis  
  aes(x = brand) +
  # make a histogram  
  geom_bar(color = "black", fill = "pink") +
  labs(x= "brand") +
  # add non-default theme of choice
  theme_bw() 


```
### Answer

The brands of ramen in Australia have are Fantastic, Maggi, Singa-Me, Suimin and Trident.


<br><br>

## Question 4

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods
```{r}

#ramen_ratings %>%
  #drop_na(brand) %>%
  #filter(brand = "Myojo") %>% 
  #ggplot() + 
  # style on x axis  
  #aes(x = brand) +
  # make a histogram  
  #geom_bar(color = "black", fill = "pink") +
  #labs(x= "brand") +
  # add non-default theme of choice
  #theme_bw()



```
### Answer

Replace this text with your answer to your question.
