---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Alexis Kulbacki"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
# load library
library(tidyverse)
```

<br><br>

## Introduction

```{r read-examine-data}
# reading in the data 
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv")
```

<br><br>

## Question 1

#### In Japan, what is the most frequent number of star ratings?

### Methods
```{r}
# view the data
glimpse(ramen_ratings)

# pipe in the data
ramen_ratings %>%
  # drop rows with no answer for stars
   drop_na(stars) %>%
  # filter the country to be Japan
  filter(country == "Japan", style %in% c("cup", "pack", "tray", "bowl")) %>%
  # select specific rows, in this case stars and country 
  select(stars, country, style) -> ramen_data1

# pipe in the wrangled data
ramen_data1 %>%
# ggplot function
ggplot() + 
  # style on x axis  
  aes(x = style, y = stars) +
  # make a histogram  
  geom_col(color = "black", fill = "pink") +
  labs(x= "number of stars") +
  # add non-default theme of choice
  theme_bw() -> ramen_histogram

print(ramen_histogram)

```
### Answer

Replace this text with your answer to your question.


<br><br>

## Question 2

#### In China, what packaging style of ramen seems to be the favorite?

### Methods
```{r}

ramen_ratings %>%
  drop_na(style) %>%
  filter(country == "China") -> ramendata2

ramendata2 %>%
ggplot() + 
  # style on x axis  
  aes(x = style) +
  # make a histogram  
  geom_bar(stat = "count", color = "black", fill = "pink") +
  labs(x= "style") +
  # add non-default theme of choice
  theme_bw() 



```
### Answer

In China, the ramen packaging style that most people seem to like is pack.

<br><br>

## Question 3

#### Between the three brands of ramen Yum Yum, Nagatanien, Acecook, what is the most frequently sold.

### Methods
```{r}

#ramen_ratings %>%
  #drop_na(brand) %>%
  #filter(country == Thailand, brand == "Yum Yum", "	Nagatanien") 
  #select(country, brand) %>%
  #ggplot() + 
  # style on x axis  
  #aes(x = brand) +
  # make a histogram  
  #geom_bar(color = "black", fill = "pink") +
  #labs(x= "brand") +
  # add non-default theme of choice
  #theme_bw() 


```
### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods
```{r}




```
### Answer

Replace this text with your answer to your question.
